\documentclass{article}

% if you need to pass options to natbib, use, e.g.:
% \PassOptionsToPackage{numbers, compress}{natbib}
% before loading nips_2016
%
% to avoid loading the natbib package, add option nonatbib:
% \usepackage[nonatbib]{nips_2016}

%\usepackage{nips_2016}

% to compile a camera-ready version, add the [final] option, e.g.:
% \usepackage[final]{nips_2016}

\usepackage[utf8]{inputenc} % allow utf-8 input
\usepackage[T1]{fontenc}    % use 8-bit T1 fonts
\usepackage{hyperref}       % hyperlinks
\usepackage{url}            % simple URL typesetting
\usepackage{booktabs}       % professional-quality tables
\usepackage{amsfonts}       % blackboard math symbols
\usepackage{nicefrac}       % compact symbols for 1/2, etc.
\usepackage{microtype}      % microtypography

\title{Feature Selection in Finance}
\usepackage[final]{nips_2016}

% The \author macro works with any number of authors. There are two
% commands used to separate the names and addresses of multiple
% authors: \And and \AND.
%
% Using \And between authors leaves it to LaTeX to determine where to
% break the lines. Using \AND forces a line break at that point. So,
% if LaTeX puts 3 of 4 authors names on the first line, and the last
% on the second line, try using \AND instead of \And before the third
% author name.

\author{
  Benjamin A. Schifman, Justin J. Siekmann\\
  Department of Electrical and Computer Engineering\\
  University of Arizona\\
  Tucson, AZ 85719 \\
  \texttt{bschifman@email.arizona.edu} \\
  \texttt{jsiekmannemail.arizona.edu}
  %% examples of more authors
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \AND
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
  %% \And
  %% Coauthor \\
  %% Affiliation \\
  %% Address \\
  %% \texttt{email} \\
}

\begin{document}
 

\maketitle

\begin{abstract}
  The abstract paragraph should be indented \nicefrac{1}{2}~inch
  (3~picas) on both the left- and right-hand margins. Use 10~point
  type, with a vertical spacing (leading) of 11~points.  The word
  \textbf{Abstract} must be centered, bold, and in point size 12. Two
  line spaces precede the abstract. The abstract must be limited to
  one paragraph.
\end{abstract}

\section{Introduction}
\indent We explore different approaches to apply machine learning principles and algorithms to the financial industry. There exist technical indicators traditionally used by analysts to evaluate and predict market and equity performance, as they “can provide a unique perspective on the strength and direction of the underlying price action” ({\bf <--what is this quote from??}). Feature extraction could be used to determine relevant indicators while identifying irrelevant and redundant indicators. Different implementations of algorithms based on these indicators could be used to predict performance of individual equities, sectors, or overall markets. They could also be used to classify and identify the correlation and interdependencies between equities, sectors, and markets. Our goal is to implement these various approaches to determine their efficacy as enablers to financial analysis. The biggest obstacle we face is finding relevant  and ways to accurately test our implementations. This being said, below are extensive datasets on stock market pricing and volume data that will serve as the basis in generating technical indicator features to implement in our machine learning algorithms. From this project we hope to deepen our understanding of the usage cases for applying specific machine learning algorithms as well as expanding upon our technical analysis of the stock market and which indicators play a role in successful market analysis.

\section{Related Work}
This is optional. If wanted, save til last.
\section{Methods/Approach}
\subsection{Normalization}
\subsection{Maximal Information Coefficient}
The Maximal Information Coefficient (MIC) is "a measure of two-variable dependence designed specifically for rapid exploration of many-dimensional data sets" - http://www.exploredata.net/. A benefit to MIC correlations between two variables is that it can be described regardless of linear or non-linear relationships. The MIC yields a single vale $0 \leq MIC \leq 1$ with a value closer to $1$ representing that the variables are more closely correlated, and a value near $0$ indicates statistically independent variables that have neither linear nor nonlinear relationships. The $minepy$ library was used in python to rank the features according to their MIC with the target variable. The MIC was calculated for each feature in each ticker, and then a final MIC value for each feature was calculated by taking the mean of the values.

\section{Results}
\section{Conclusion}

\section*{References}

References follow the acknowledgments. Use unnumbered first-level
heading for the references. Any choice of citation style is acceptable
as long as you are consistent. It is permissible to reduce the font
size to \verb+small+ (9 point) when listing the references. {\bf
  Remember that you can use a ninth page as long as it contains
  \emph{only} cited references.}
\medskip

\small

[1] Alexander, J.A.\ \& Mozer, M.C.\ (1995) Template-based algorithms
for connectionist rule extraction. In G.\ Tesauro, D.S.\ Touretzky and
T.K.\ Leen (eds.), {\it Advances in Neural Information Processing
  Systems 7}, pp.\ 609--616. Cambridge, MA: MIT Press.

[2] Bower, J.M.\ \& Beeman, D.\ (1995) {\it The Book of GENESIS:
  Exploring Realistic Neural Models with the GEneral NEural SImulation
  System.}  New York: TELOS/Springer--Verlag.

[3] Hasselmo, M.E., Schnell, E.\ \& Barkai, E.\ (1995) Dynamics of
learning and recall at excitatory recurrent synapses and cholinergic
modulation in rat hippocampal region CA3. {\it Journal of
  Neuroscience} {\bf 15}(7):5249-5262.

\end{document}